---
title       : Developing-data-products 
subtitle    : Introduce to the shinyapp I create
author      : Wang
job         : Penn State
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Outline

1, what I do

I make a shinyApp with interative interface by using shiny package. THe shinyApp is about how to check stock price in a time range.


2. origin of data

I select three stocks: AAPL, GLID and NFLX. The data is loaded through package "quantmod" from yahoo!

3, shinyApp interface

The interface includes checkboxs, textboxs, a radio button and a slider

--- .class #id 

## Plot of stock price vs. time 
This slide is used to show that how a stock price(Here I use AAPL for an example) evolves as time
```{r echo= TRUE,results=FALSE,cache = FALSE}
library(png); localPNG <- readPNG("./stock1.png");plot(1)
rasterImage(localPNG, 0.6, 0.6, 1.4, 1.4)
```


--- .class #id 

## Plot of stock price vs. time with a slider to change the price
This plot is to show that I add a slider to indicates the price.
```{r echo= TRUE,results=FALSE,cache = FALSE}
library(png); localPNG <- readPNG("./stock2.png");plot(1)
rasterImage(localPNG, 0.6, 0.6, 1.4, 1.4)
```


--- .class #id 

## Interface of shinyApp
Check the link to play around the interactive shinyapp: https://gavin0wang.shinyapps.io/Develop-Data-Product

```{r echo = TRUE, results = FALSE, cache= FALSE}
library(png);localPNG <- readPNG("./stock.png");plot(1)
rasterImage(localPNG, 0.6, 0.6, 1.4, 1.4)
```

